\documentclass[11pt, a4paper, twoside]{Thesis}
\usepackage{etex}
%\usepackage{arabtex}
%\usepackage{utf8}

%\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tocbibind}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{multirow}
\usepackage{subfig}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning}

\usetikzlibrary{arrows}

\usetikzlibrary{shapes.geometric, arrows}
\usepackage{microtype}

\usepackage{standalone}
\usepackage{tabularx}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

\setlength{\parindent}{0.7cm}
\setlength{\tabcolsep}{0.2em}
\def\arraystretch{1}

\makeatletter
\DeclareRobustCommand\onedot{\futurelet\@let@token\@onedot}
\def\@onedot{\ifx\@let@token.\else.\null\fi\xspace}

\newif\ifdraft\drafttrue
\drafttrue
\ifdraft
\newcommand{\cm}[1]{{\textcolor{red}{ *COMMENT: #1 * }}}
\else
\newcommand{\cm}[1]{}
\fi

\def\eg{\emph{e.g}\onedot} \def\Eg{\emph{E.g}\onedot}
\def\ie{\emph{i.e}\onedot} \def\Ie{\emph{I.e}\onedot}
\def\cf{\emph{c.f}\onedot} \def\Cf{\emph{C.f}\onedot}
\def\etc{\emph{etc}\onedot} \def\vs{\emph{vs}\onedot}
\def\wrt{w.r.t\onedot} \def\dof{d.o.f\onedot}
\def\etal{\emph{et al}\onedot}
\usepackage[group-separator={,}]{siunitx}

\renewcommand{\G}{\ensuremath{\mathcal{G}}\xspace}
\newcommand{\X}{\ensuremath{\mathcal{X}}\xspace}
\renewcommand{\C}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\R}{\ensuremath{\mathcal{R}}\xspace}
\newcommand{\PG}{\ensuremath{\mathcal{P}}\xspace}
\newcommand{\PW}{\ensuremath{\mathsf{PW}}\xspace}
\newcommand{\sem}[1]{[|#1|]}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\incl}{\subseteq}
\renewcommand{\L}{\ensuremath{\mathcal{L}}\xspace}

\makeatother

\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\abs}[1]{\left\lvert#1\right\rvert}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\listofalgorithmes}{\tocfile{\listalgorithmcfname}{loa}}
\newcommand\Chapter[2]{
  \chapter[#1: {\itshape#2}]{#1\\[1ex]\Large#2}
}

\begin{document}
\input{commands}
%\setcode{utf8}

% *************** Front matter ***************
\frontmatter

\title  {An Embedding-based Approach to\\ 
Rule Learning from Knowledge Graphs}

\authors  {\texorpdfstring
            {{Vinh Thinh Ho}}
            {}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
%\usdate
\date       {Saarbr\"ucken, \today }
\subject    {}
\keywords   {}

\maketitle

%\newpage
%\mbox{}
%\thispagestyle{empty}
%\newpage

\setstretch{1.3}

\thispagestyle{empty}

\section*{Eidesstattliche Erkl\"{a}rung}
Ich erkl\"{a}re hiermit an Eides Statt, dass ich die vorliegende Arbeit selbstst\"{a}ndig verfasst und keine
anderen als die angegebenen Quellen und Hilfsmittel verwendet habe.

\vspace{0.60cm}
\section*{Statement in Lieu of an Oath}
I hereby confirm that I have written this thesis on my own and that I have not used any other media or
materials than the ones referred to in this thesis.
\vspace{1.5cm}

\section*{Einverst\"{a}ndniserkl\"{a}rung}
Ich bin damit einverstanden, dass meine (bestandene) Arbeit in beiden Versionen in die Bibliothek der
Informatik aufgenommen und damit ver\"{o}ffentlicht wird.

\vspace{0.60cm}
\section*{Declaration of Consent}
I agree to make both versions of my thesis (with a passing grade) accessible to the public by having
them added to the library of the Computer Science Department.
\vspace{3cm}

\begin{flushright}
\noindent Saarbr\"{u}cken, \today
\hfill
Vinh Thinh Ho
\end{flushright}

\clearpage  % Declaration ended, now start a new page
%% ----------------------------------------------------------------

\newpage
\mbox{}
\thispagestyle{empty}
\newpage

% The Abstract Page
\input{abstract}
%% ----------------------------------------------------------------
\newpage
\mbox{}
\thispagestyle{empty}
\newpage

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
First of all, I would like to give my special thanks to Dr. Daria Stepanova for guiding me to complete my master thesis. She not only gave me a plenty of ideas for my thesis, but also sent me so much energy and enthusiasm when I was in the hardest time. To me, she is an ideal supervisor, I would not have been able to finish this thesis without her help.

I also want to say thanks to Prof. Dr. Gerhard Weikum, Dr. Evgeny Kharlamov and Mohamed H. Gad-Elrab for cooperating with me to successfully publish a paper in the \textit{ISWC'18} conference.

I am also thankful for the support from Dang during my master life. He is not only my friend, my teammate, my senior, but also my brother, who helped me a lot in my career life.

Lastly but most importantly, I want to send a sincere thanks to my grandparents, my parents, my brother, who are always besides me, providing me with love and encouragement to continually push myself to succeed.
\addtocontents{toc}{}  % Add a gap in the Contents, for aesthetics    \vspace{1em}

}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------
\newpage
\mbox{}
\thispagestyle{empty}
\newpage

\newpage
\mbox{}
\thispagestyle{empty}
\newpage

\setstretch{1}
\begin{spacing}{0.1}
\pagestyle{fancy}
\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage
%\listofalgorithmes
\end{spacing}

\clearpage

\setstretch{1.3}
% *************** Main matter ***************
\mainmatter

\input{chapters/intro}

\input{chapters/relatedwork}

\input{chapters/preliminaries}

\input{chapters/methodology}

\input{chapters/implementation}

\input{chapters/evaluation}

\input{chapters/conclusion}

%\input{chapters/system}

% *************** Bibliography ***************
\bibliographystyle{plain}
{\small\bibliography{bibliography/reference}}
\clearpage

% *************** Appendixes ***************
\addtocontents{toc}{\vspace{2em}}
\appendix
%\appendixpage*


% *************** Back matter ***************
%\backmatter
%\input{back.tex}

\end{document}